### 2013-05-02 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
sttarting work on spn spatial discretization

(e.g. $\phi_6 = \phi_4 = 0$ yields the $SP_3$ equations).

@@

%%---------------------------------------------------------------------------%%
\section{Spatial Discretization}
\label{sec:spatial_discretization}
To this point, the formulation of the multigroup $SP_N$ equations
presented have discretized the transport equation in angle and energy
but have yet to consider the spatial component of phase space. We
don't explicitly consider it in this document but instead we will
briefly comment on possible means of discretization. Of primary
interest here is the discretization of the diffusive term in
Eq~(\ref{eq:spn_multigroup_system}) and the convective term on the
boundaries in Eq~(\ref{eq:spn_multigroup_bnd}). Many popular choices
for spatial discretization are available here and include finite
difference and finite element formulations. In the Denovo package at
ORNL, Evans has implemented a finite volume scheme for these
equations. Although arbitrary grids could be handled effectively
through a finite element scheme, the rectilinear grid used in Denovo
is easily discretized through the finite volume method in a
conservative form. This conservative form is ideal for the
diffusion-like equations in the domain given by
Eq~(\ref{eq:spn_multigroup_system}) and the effective boundary current
conditions given by Eq~(\ref{eq:spn_multigroup_bnd}) as the neutron
current is balanced from cell-to-cell, continuity of the flux is
preserved across cell/material boundaries, and boundary conditions are
naturally represented through cell-face currents. Furthermore, this
spatial discretization is a natural extension of the balance
principles used to arrive at the general transport equation.

>>>>

(e.g. $\phi_6 = \phi_4 = 0$ yields the $SP_3$ equations). Boundary
conditions for these equations are provided in
Appendix~\ref{chap:spn_boundary_conditions}.

@@

Boundary conditions for these equations are provided in
Appendix~\ref{chap:spn_boundary_conditions}.

%%---------------------------------------------------------------------------%%
\subsection{Spatial Discretization}
\label{subsec:spatial_discretization}
To this point, the formulation of the multigroup $SP_N$ equations
presented have discretized the transport equation in angle and energy
but have yet to consider the spatial component of phase space. We
don't explicitly consider it in this document but instead we will
briefly comment on possible means of discretization. Of primary
interest here is the discretization of the diffusive term in
Eq~(\ref{eq:spn_multigroup_system}) and the current term on the
boundaries in Eq~(\ref{eq:spn_multigroup_bnd}). Many popular choices
for spatial discretization are available here and include finite
difference and finite element formulations. In the Denovo package at
ORNL, Evans has implemented a finite volume scheme for these
equations resulting in:
\begin{equation}

  \label{eq:spn_spatial_discretization}
\end{equation}
Although arbitrary grids could be handled effectively
through a finite element scheme, the rectilinear grid used in Denovo
is easily discretized through the finite volume method in a
conservative form. This conservative form is ideal for the
diffusion-like equations in the domain given by
Eq~(\ref{eq:spn_multigroup_system}) and the effective boundary current
conditions given by Eq~(\ref{eq:spn_multigroup_bnd}) as the neutron
current is balanced from cell-to-cell, continuity of the flux is
preserved across cell/material boundaries, and boundary conditions are
naturally represented through cell-face currents. Furthermore, this
spatial discretization is a natural extension of the balance
principles used to arrive at the general transport equation.
